---
page-layout: full
---

::: {.banner}

::: {.centered}
# Code projects by Danielle Navarro
:::

:::

At various times in my life I have released code I wrote into the wild. Usually on purpose, occasionally by accident, but almost always with my blessings. Sometimes that code is reused by other people. The most widely-used code I have ever written in my life appears in Appendix C to an obscure paper on the computation of first passage to absorbtion times for Weiner diffusion processes. The original manuscript is [here](https://papers.djnavarro.net/2009_firstpassage.pdf) and you need to scroll down to page 19 to find it. The code is written in MATLAB syntax and -- just to make things worse -- there's actually a bug in code. If you take the code at face value it simply doesn't work. Nevertheless, some versions of this code have found their way into an astonishing range of scientific software tools. This one silly little snippet, barely more than a github gist, is in fact the most contagiously viral bit of code I've ever written. But it's not software, right? It doesn't have a github repo, and you can't install it with apt get. It's just... code. And so, with this ambiguity stated up front, here is an incomplete and idiosyncratic list of "weird things Danielle has done with code that have sometimes been used by others". It is a random grab-bag of things I have done with code that others might maybe want to also do with code. No more, no less.

## Pharmacometrics tools

## 

```{r}
#| echo: false
add_card <- function(src, title, text, url, link_text, img_alt) {
  lines <- c(
    '<div class="g-col-12 g-col-md-6 g-col-xl-4">',
    '<div class="card h-100">',
    paste0(
      '<a href="', 
      url, 
      '"><img src="', 
      src, 
      '"',
      'alt = "',
      img_alt,
      '"',
      'class="card-img-top"></a>'
    ),
    '<div class="card-body">',
    paste0('<h2 class="card-title">', title, '</h2>'),
    paste0('<p class="card-text">', text, '</p>'),
    '</div>',
    '<div class="card-footer">',
    paste0('<a href="', url, '" class="btn btn-primary">', link_text, '</a>'),
    '</div>',
    '</div>',
    '</div>'
  )
  cat(lines, sep="\n")
}
```


::: {.grid}

```{r}
#| echo: false
#| results: asis

```

::: 
